\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-29 syntax.tex
Fix typo.

Based upon the basic MLTT,
we will have four new kinds of judgements to model our linkages. Among them, sealing judgement $\goodSeal{\Gamma}{\_}{\sigma}{A}$ is the
most special one because it is actually just a shorthand of term
judgement $\goodTerm{\Gamma , \cL \sigma}{\_}{A[\pi_1]}$.\YZ{You haven't introduced the notation A[pi_1] yet at this point. And what is A[pi_1]?}\EDJreply{added for the intro. It is a shorthand for pi_1(id)}

@@

Sealing\YZ{It occurs to me that you use the word "sealing" to mean different (though tangentially related) things. Previously you used it as in "sealed families".}\EDJreply{They are actually the same thing. This sealing in metatheory is much stronger than that of the implemented plugin. Downside of the strong sealing is that if the user really use this version of sealing, the user will have to annotate what the sealed family type is. Now in the plugin, the sealed family type is almost fixed (directly inferred using a fixed rules). So basically this complete version of sealing (in metatheory) can deduce that of seal (in plugin implementation) } is used to exploit this fact---with sealing, given $X_1 : \bW
\sigma_1$, we can add well-typed terms $X_1 : \cU \vdash t : T$, into
the parent family. Later when we want to inherit $t$,
because $t$ only consider $X_1$ as an arbitrary type, inheritance is
possible.

>>>>

Based upon the basic MLTT,
we will have four new kinds of judgements to model our linkages. Among them, sealing judgement $\goodSeal{\Gamma}{\_}{\sigma}{A}$ is the
most special one because it is actually just a shorthand of term
judgement $\goodTerm{\Gamma , \cC \sigma}{\_}{A[\pi_1]}$.\YZ{You haven't introduced the notation A[pi_1] yet at this point. And what is A[pi_1]?}\EDJreply{added for the intro. It is a shorthand for pi_1(id)}

@@

Sealing\YZ{It occurs to me that you use the word "sealing" to mean different (though tangentially related) things. Previously you used it as in "sealed families".}\EDJreply{They are actually the same thing. This sealing in metatheory is much stronger than that of the implemented plugin. Downside of the strong sealing is that if the user really use this version of sealing, the user will have to annotate what the sealed family type is. Now in the plugin, the sealed family type is almost fixed (directly inferred using a fixed rules). So basically this complete version of sealing (in metatheory) can deduce that of seal (in plugin implementation) } is used to exploit this fact---with sealing, given $X_1 : \bW
\sigma_1$, we can add well-typed terms $X_1 : \cU \vdash t : T$, into
the parent family. Later when we want to inherit $t$,
because $t$ only consider $X_1$ as an arbitrary type, inheritance is
possible. This sealing is the general version of the sealed family implemented in the plugin. Our plugin will deduce a sealed ``interface'' for a sealed family using a fixed set of rules but here sealing in metatheory can be arbitrary local morphism.
